---
title: "Lab 00 - Hello IDS!"
author: "INSERT YOUR NAME HERE"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Chinedut", "Tommy", "Aaron", 
           "Luianda", "Abdullah"),
  github_username = c("Chinedut26", "Tommys262550", "Aaron2405", 
                      "LuiandaMadwa", "AbdullahS06"), 
  colour = c("Purple", "Red", "Red", 
             "Blue", "Red"),
  hobby = c("Running", "Football", "Running", 
            "Music", "Music"),
  favourite_number = c(5, 8, 3, 6, 7)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


The plot shows the usernames along with their favourite colour and number

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Insert text here", 
          y = "Insert text here",
          title = "Insert text here")
```

Labs() modifys the "x" and "y" axis

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

*Remove this text (including the stars) and add your answer for Exercise 20 here.*
